---
title: "runoff_volume"
output: html_document
---
# loading libraries
```{r}
library(here)
library(tidyverse)
```

# Make a function, source
```{r}
source(here::here("src","storm_runoff.R"))
```

# In a code chunk in your runoff_volumes.Rmd, use your predict_runoff function to estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01). Note: you do not need to write a for loop here.
```{r}
volume_seq <- seq(from= 0.6, to = 0.8, by=0.01)

volume <- predic_runoff(I_a = volume_seq, A= 182) #outcome= 2.3

```
*Bind your sequence* of impervious fractions together with the resulting runoff volume calculated into a data frame
```{r}
stormwater_volume_df <-data.frame(volume)
```

# Create a ggplot graph that has both dots and connecting lines (i.e., you’ll layer geom_point() and geom_line()). Update axis labels. Export a png of your graph to the figs folder using ggsave.
```{r}
Storm_water_plot <- ggplot(data= stormwater_volume_df, aes(x= volume,y= volume_seq))+
  geom_point()+
  geom_line()

# SAVE PLOT AS PNG
ggsave(here::here("figs","Storm_water_plot.png"),
       width = 6, height = 7)
```


